%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Procter \& Gamble} % Organization
    {Beijing, China} % Location
    {Jul 2020 \textemdash Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and optimized data pipelines to fetch, extract, process, and store data from all kinds of data sources: csv/Excel, PowerPoints, videos, images, audios, and third-party data APIs.}
        \item {Designed and built multiple Django/Flask API servers using Docker and integrated in-house machine learning/deep learning models into processing pipelines.}
        \item {Developed mutiple frontend interfaces, using either ReactJS or server-side rendering. Provided user-friendly interface for features like basic CRUD, OAuth authentication, single/batch upload, video and metadata interactions, etc.}
        \item {Maintained API documents using Swagger and wrote testing and migration scripts.}
        \item {Deployed a centralized monitoring environment(on-premise Sentry), which gathers the system metrics and obtains bug reports and preformance measures.}
        \item {Communicated with multiple business units to align requirements with product researchers, create project plans, and manage final deliverables.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Backend Developer} % Job title
    {LeQi Technology Co., Ltd.} % Organization
    {Wuxi, China} % Location
    {Jan 2019 \textemdash Jun 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed RESTful API server for location-based lottery disbursement, promotions and campaigns.}
        \item {Integrated and tested SDK updates of third-party payment platforms and implemented the sandbox environment for testing purposes.}
        \item {Built admin dashboards to visualize sales data and consumer demographics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer} % Job title
    {Unisoc Communications, Inc} % Organization
    {Nanjing, China} % Location
    {Apr 2017 \textemdash Dec 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed native applications for Android system (4.4 to 8.0), targeting low-end Android devices.}
        \item {Integrated applications with SAF(Storage Access Framework), SELinux for Google's "Project Treble" support.}
        \item {Developed continuous integration scripts to achieve automated pressure test.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
